A Comparison of Dimensionality Reduction Techniques for Robotic Motion Planning

### 2016-05-11 paper/paper.tex
added to paper

We used Feature Agglomeration, Truncated SVD, PCA, Kernel PCA, Randomized PCA, and
our own "Trained Johnson-Lindestrauss" to perform dimensionality reduction. We will briefly summarize each of these techniques.

@@

Truncated SVD:

>>>>

We used Feature Agglomeration, Truncated SVD, PCA, Kernel PCA, Randomized PCA, and
our own "Trained Johnson-Lindenstrauss" to perform dimensionality reduction. We will briefly summarize each of these techniques.

@@

Truncated SVD: Truncated SVD works best with sparse matrices.

Trained Johnson-Lindenstrauss: Normal Johnson-Lindenstrauss uses a random mxn Gaussian matrix to reduce the dimensionality of a vector from n to m. Instead of using a random matrix, we train a matrix on randomly-generated obstacles in n-space to minimize [MINIMIZE WHAT?]

Methods:
